Privacy-Preserving Localisation Using Private Linear-Combination Aggregation

### 2020-11-09 main.tex
Small typo in equation
First pass-through for new symbols (making characters more unique across the work as requested) Also added some re-definitions for lambda and kappa as these were not clear Made a bunch of brackets and vertical bars use left/right/middle to be sized properly Fixed up the text in the Algorithms a tiny bit Changed rational definitions equations a little (equivalent but easier to read)

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

@@

\subsection{Notation}
Throughout this work, we will use the following notation. Lowercase characters are scalars, $a$, vectors are underlined, $\vec{a}$, and random variables are bold, $\rv{a}$. Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose. $|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector normal. Subscripts $\rv{x}_{k|j}$ will denote an estimate of $\rv{x}_k$ using measurements from times up to and including $j$. $\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$. Additionally, key $k$ may be ommited when inferrable from context. $\lfloor\cdot\rceil$ rounds to the nearest integer, $a\|b$ stands for a bitwise concatenation of $a$ and $b$ and sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.

@@

To support multiple aggregations at each time-step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by $t$. The desired bi-direction communication protocol at instance $t$ consists of of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator. That is, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator. This has been summarised in Figure \ref{fig:agg_steps}.
\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize]
    % Step 1
    \node at (3.25,5.5) {1. Broadcast and combination step};
    % Navigator
    \fill (3.25,4.5) [blue!40] ellipse (0.4 and 0.4);
    \pic[xscale=0.22,yscale=0.3] at (3.25,4.6725) {plane};
    % Sensors
    \node at (1.5,0.375) {Sensor $1$};
    \fill [red!40] (0.25,0.625) rectangle (2.875,1.625);
    \node at (1.625,1.125) {$\displaystyle y_1^{(t)} \!=\! \sum^m_{j=1}x_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (5,0.375) {Sensor $n$};
    \fill [red!40] (3.625,0.625) rectangle (6.25,1.625);
    \node at (5,1.125) {$\displaystyle y_n^{(t)} \!=\! \sum^m_{j=1}x_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (3.5,1.125) circle (0.05);
    \fill [black] (3,1.125) circle (0.05);
    \fill [black] (3.25,1.125) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4) (5,1.875)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4) (1.5,1.875)};
    \fill [lightgray] (2.125,3.375) rectangle (4.375,2.625);
    \node at (3.25,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};

    % Step 2
    \node at (3.25,-0.75) {2. Aggregation step};
    % Navigator
    \fill [blue!40] (1.375,-3) rectangle (5.125,-1.25);
    \pic[xscale=0.22,yscale=0.3] at (3.25,-1.4775) {plane};
    \node at (3.25,-2.375) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}y^{(t)}_{i}$};
    % Sensors
    \node at (1.25,-5.875) {Sensor $1$};
    \fill  (5.25,-5.25) [red!40] ellipse (0.4 and 0.4);
    \node at (5.25,-5.875) {Sensor $n$};
    \fill  (1.25,-5.25) [red!40] ellipse (0.4 and 0.4);
    \fill [black] (2.75,-5.25) circle (0.05);
    \fill [black] (3.75,-5.25) circle (0.05);
    \fill [black] (3.25,-5.25) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(5,-4.75) (3.75,-3.25)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.5,-4.75) (2.75,-3.25)};
    \fill [lightgray] (1.625,-3.75) rectangle (2.25,-4.25);
    \node at (2,-4) {$y_1^{(t)}$};
    \fill [lightgray] (4.25,-3.75) rectangle (4.875,-4.25);
    \node at (4.625,-4) {$y_n^{(t)}$};

@@

\begin{remark}
    From the aggregation definition above and the distributive property of real numbers, it is clear that an alternative method to the bi-directional communication requirement would be computing $\sum^{m}_{j=1}\omega_j^{(t)}\sum^{n}_{i=1} x_{i,j}^{(t)}$ by the navigator, requiring only uni-directional communication by sending values $x_{i,j}^{(t)}, 1 \leq j \leq m$ from each sensor $i$. We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in Section \ref{subsec:algorithm}.
\end{remark}

@@

Encryption of a plaintext message $m \in \mathbb{Z}_N$, producing ciphertext $c \in \mathbb{Z}^{*}_{N^2}$, is computed by
\begin{equation}
    c = g^m r^N \pmod{N^2}
\end{equation}
for a randomly chosen $r \in \mathbb{Z}_{N}$. $r^N$ can be considered the noise term which hides the value $g^m \pmod{N^2}$, which due to the scheme construction, is an easily computable discrete logarithm. The decryption of a ciphertext is computed by
\begin{equation}
    m = \frac{L(c^\lambda\pmod{N^2})}{L(g^\lambda\pmod{N^2})} \pmod{N}
\end{equation}
where $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{N}$.

In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall m_1,m_2 \in \mathbb{Z}_N$,
\begin{align}
    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2) \hspace{-7pt} \pmod{N^2}) &= m_1+m_2 \hspace{-7pt} \pmod{N} \\
    \mathcal{D}(\mathcal{E}(m_1)g^{m_2} \hspace{-7pt} \pmod{N^2}) &= m_1+m_2\hspace{-7pt}\pmod{N} \label{eqn:paillier_hom_plain_add}\\
    \mathcal{D}(\mathcal{E}(m_1)^{m_2} \hspace{-7pt} \pmod{N^2}) &= m_1m_2 \hspace{-7pt} \pmod{N}\,. \label{eqn:paillier_hom_mult}
\end{align}

@@

Encryption of plaintext $m^{(t)}_{i} \in \mathbb{Z}_N$ to ciphertext $c^{(t)}_{i} \in \mathbb{Z}_{N^2}$ at instance $t$ is computed by user $i$ as
\begin{equation}
    c^{(t)}_{i} = (N+1)^{m^{(t)}_{i}} H(t)^{sk_i} \pmod{N^2}\,,
\end{equation}
where the $H(t)^{sk_i}$ can be considered the noise term which hides the again easily computable discrete logarithm $g^{m^{(t)}_{i}} \pmod{N^2}$, where $g=N+1$.

When all encryptions $c^{(t)}_{i},\,1\leq i \leq n$ are sent to the aggregator, summation and decryption are computed by the functions
\begin{equation}
    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2}
\end{equation}
and
\begin{equation}
    \sum^{n}_{i=1}m^{(t)}_{i} = \frac{c^{(t)}-1}{N}\,. \label{eqn:agg_decryption}
\end{equation}
Correctness follows from $\sum^{n}_{i=0}sk_i = 0$, and thus
\begin{equation*}
    \begin{split}
        &H(t)^{sk_0}\prod^{n}_{i=1}c_{i,t} \pmod{N^2} \\
        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{m_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}g^{m_{i,t}} \pmod{N^2} \\
        \equiv &(N+1)^{\sum^n_{i=1}m_{i,t}} \pmod{N^2}
    \end{split}
\end{equation*}
removing all noise terms.

@@

\section{Private Linear-Combination Aggregation} \label{sec:lcao_definition}
As stated in Section \ref{subsec:problem_decomposition}, we decompose the localisation method such that the multi-party aggregation protocol, given in Figure \ref{fig:agg_steps}, captures all communication between the navigator and sensors. To perform this protocol in a secure manner, we must first describe the security properties we aim to achieve during aggregation. Broadly speaking, we want a cryptographic scheme which allows instances of homomorphically computed linear combinations of encrypted weights, to be summed by a private aggregation scheme. That is, we do not want sensors to learn the navigator weights, while we do not want the navigator to learn individual weighted linear combinations. This can be summarised by the two informal security notions:
\begin{LaTeXdescription}
    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
    \item[Private Linear-Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ from the current and previous instances. Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}y_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} x^{(t)}_{i,j}\omega^{(t)}_j$.
\end{LaTeXdescription}

\begin{remark} \label{rem:lcao_leakage}
    The notion of a leakage function including parameters from the aggregator requires extra care to be taken when giving its definition. Since an attacker may compromise the aggregator, they have control over the choice of these parameters, and therefore over the leakage function. We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.} $\sum^m_{j=1}x^{(t)}_{i,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $x^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
\end{remark}

@@

\subsection{Linear-Combination Aggregator Oblivious Encryption} \label{subsec:lcao}
We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$. These are used by a trusted third party, an aggregator and value producing users $i\,1\leq i \leq n$. They are defined as follows

\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the number of weights $m$, the aggregator's public and private keys $pk_0$ and $sk_0$, and the user private keys $sk_i,\,1\leq i \leq n$.
    \item[$\mathsf{Enc}(pk_0, a)$] The aggregator and users can encrypt any value $a$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(a)$.
    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] At instance $t$, user $i$ computes and obtains the encrypted linear combination $y^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}y_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} x^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
\end{LaTeXdescription}

@@

\begin{LaTeXdescription}
    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
    \begin{LaTeXenumerate}
        \item \textit{Encryption:} The attacker chooses a value $a$ and computes an encryption of $a$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(a)$.
        \item \textit{Weight Queries:} The attacker chooses an instance $t$ and receives the weights for that instance encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ and $(i',t',x^{\prime(t')}_{i',1},\dots,x^{\prime(t')}_{i',m})$, the following condition holds:
        \begin{equation*}
            i = i' \wedge t = t' \implies x^{(t)}_{i,m} = x^{\prime(t')}_{i',m},\,1\leq j\leq m\,.
        \end{equation*}
        The attacker is then given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{LaTeXenumerate} 
    \item[Challenge] Next, the attacker chooses an instance $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for the instance $t^*$, and no compromise queries, are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
    \end{equation*}
    and
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.} the aggregator is compromised) and $S = U$, it is additionally required that
    \begin{equation*}
        \sum_{i\in S}\sum^{m}_{j=1} x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
    \end{equation*}
    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen instance $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j)\,|\,i\in S\rangle\,.
    \end{equation*}
    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game if and only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{LaTeXdescription}

\begin{definition}
    An encryption scheme meets LCAO security if no adversary, running in probabilistic-time with respect to security parameter, has more than a negligible advantage in winning the above security game. Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
\end{definition}

@@

    \For{$v \gets 1$ to $2$}
        \State Receive $\beta_{v1}^{(i)}$ from each sensor $1\leq i \leq n$
    \EndFor

>>>>

% If you want to put a publisher's ID mark on the page you can do it like this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

@@

\subsection{Notation}
Throughout this work, we will use the following notation. Lowercase underlined characters are vectors, $\vec{a}$, and random variables are bold, $\rv{a}$. Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose. $|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector normal. Subscripts $\rv{x}_{k|j}$ will denote an estimate of $\rv{x}_k$ using measurements from times up to and including $j$. $\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$. Additionally, key $k$ may be ommited when inferrable from context. $\lfloor\cdot\rceil$ rounds to the nearest integer, $a\|b$ stands for a bitwise concatenation of $a$ and $b$ and sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.

@@

To support multiple aggregations at each time-step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by $t$. The desired bi-direction communication protocol at instance $t$ consists of of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator. That is, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are broadcast by the navigator, linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator. This has been summarised in Figure \ref{fig:agg_steps}.
\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize]
    % Step 1
    \node at (3.25,5.5) {1. Broadcast and combination step};
    % Navigator
    \fill (3.25,4.5) [blue!40] ellipse (0.4 and 0.4);
    \pic[xscale=0.22,yscale=0.3] at (3.25,4.6725) {plane};
    % Sensors
    \node at (1.5,0.375) {Sensor $1$};
    \fill [red!40] (0.25,0.625) rectangle (2.875,1.625);
    \node at (1.625,1.125) {$\displaystyle l_1^{(t)} \!=\! \sum^m_{j=1}a_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (5,0.375) {Sensor $n$};
    \fill [red!40] (3.625,0.625) rectangle (6.25,1.625);
    \node at (5,1.125) {$\displaystyle l_n^{(t)} \!=\! \sum^m_{j=1}a_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (3.5,1.125) circle (0.05);
    \fill [black] (3,1.125) circle (0.05);
    \fill [black] (3.25,1.125) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4) (5,1.875)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4) (1.5,1.875)};
    \fill [lightgray] (2.125,3.375) rectangle (4.375,2.625);
    \node at (3.25,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};

    % Step 2
    \node at (3.25,-0.75) {2. Aggregation step};
    % Navigator
    \fill [blue!40] (1.375,-3) rectangle (5.125,-1.25);
    \pic[xscale=0.22,yscale=0.3] at (3.25,-1.4775) {plane};
    \node at (3.25,-2.375) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} a_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}l^{(t)}_{i}$};
    % Sensors
    \node at (1.25,-5.875) {Sensor $1$};
    \fill  (5.25,-5.25) [red!40] ellipse (0.4 and 0.4);
    \node at (5.25,-5.875) {Sensor $n$};
    \fill  (1.25,-5.25) [red!40] ellipse (0.4 and 0.4);
    \fill [black] (2.75,-5.25) circle (0.05);
    \fill [black] (3.75,-5.25) circle (0.05);
    \fill [black] (3.25,-5.25) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(5,-4.75) (3.75,-3.25)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.5,-4.75) (2.75,-3.25)};
    \fill [lightgray] (1.625,-3.75) rectangle (2.25,-4.25);
    \node at (2,-4) {$l_1^{(t)}$};
    \fill [lightgray] (4.25,-3.75) rectangle (4.875,-4.25);
    \node at (4.625,-4) {$l_n^{(t)}$};

@@

\begin{remark}
    From the aggregation definition above and the distributive property of real numbers, it is clear that an alternative method to the bi-directional communication requirement would be computing $\sum^{m}_{j=1}\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)}$ by the navigator, requiring only uni-directional communication by sending values $a_{i,j}^{(t)}, 1 \leq j \leq m$ from each sensor $i$. We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in Section \ref{subsec:algorithm}.
\end{remark}

@@

Encryption of a plaintext message $a \in \mathbb{Z}_N$, producing ciphertext $c \in \mathbb{Z}^{*}_{N^2}$, is computed by
\begin{equation}
    c = g^a \rho^N \pmod{N^2}
\end{equation}
for a randomly chosen $\rho \in \mathbb{Z}_{N}$. $\rho^N$ can be considered the noise term which hides the value $g^a \pmod{N^2}$, which due to the scheme construction, is an easily computable discrete logarithm. The decryption of a ciphertext is computed by
\begin{equation}
    a = \frac{L(c^\lambda\pmod{N^2})}{L(g^\lambda\pmod{N^2})} \pmod{N}
\end{equation}
where $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{N}$.

In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall a_1,a_2 \in \mathbb{Z}_N$,
\begin{align}
    \mathcal{D}(\mathcal{E}(a_1)\mathcal{E}(a_2) \hspace{-7pt} \pmod{N^2}) &= a_1+a_2 \hspace{-7pt} \pmod{N} \\
    \mathcal{D}(\mathcal{E}(a_1)g^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1+a_2\hspace{-7pt}\pmod{N} \label{eqn:paillier_hom_plain_add}\\
    \mathcal{D}(\mathcal{E}(a_1)^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1a_2 \hspace{-7pt} \pmod{N}\,. \label{eqn:paillier_hom_mult}
\end{align}

@@

Encryption of plaintext $a^{(t)}_{i} \in \mathbb{Z}_N$ to ciphertext $c^{(t)}_{i} \in \mathbb{Z}_{N^2}$ at instance $t$ is computed by user $i$ as
\begin{equation}
    c^{(t)}_{i} = (N+1)^{a^{(t)}_{i}} H(t)^{sk_i} \pmod{N^2}\,,
\end{equation}
where the $H(t)^{sk_i}$ can be considered the noise term which hides the again easily computable discrete logarithm $g^{a^{(t)}_{i}} \pmod{N^2}$, where $g=N+1$.

When all encryptions $c^{(t)}_{i},\,1\leq i \leq n$ are sent to the aggregator, summation and decryption are computed by the functions
\begin{equation}
    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2}
\end{equation}
and
\begin{equation}
    \sum^{n}_{i=1}a^{(t)}_{i} = \frac{c^{(t)}-1}{N}\,. \label{eqn:agg_decryption}
\end{equation}
Correctness follows from $\sum^{n}_{i=0}sk_i = 0$, and thus
\begin{equation*}
    \begin{split}
        &H(t)^{sk_0}\prod^{n}_{i=1}c_{i,t} \pmod{N^2} \\
        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{a_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}g^{a_{i,t}} \pmod{N^2} \\
        \equiv &(N+1)^{\sum^n_{i=1}a_{i,t}} \pmod{N^2}
    \end{split}
\end{equation*}
removing all noise terms.

@@

\section{Private Linear-Combination Aggregation} \label{sec:lcao_definition}
As stated in Section \ref{subsec:problem_decomposition}, we decompose the localisation method such that the multi-party aggregation protocol, given in Figure \ref{fig:agg_steps}, captures all communication between the navigator and sensors. To perform this protocol in a secure manner, we must first describe the security properties we aim to achieve during aggregation. Broadly speaking, we want a cryptographic scheme which allows instances of homomorphically computed linear combinations of encrypted weights, to be summed by a private aggregation scheme. That is, we do not want sensors to learn the navigator weights, while we do not want the navigator to learn individual weighted linear combinations. This can be summarised by the two informal security notions:
\begin{LaTeXdescription}
    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
    \item[Private Linear-Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $a^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances. Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$.
\end{LaTeXdescription}

\begin{remark} \label{rem:lcao_leakage}
    The notion of a leakage function including parameters from the aggregator requires extra care to be taken when giving its definition. Since an attacker may compromise the aggregator, they have control over the choice of these parameters, and therefore over the leakage function. We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.} $\sum^m_{j=1}a^{(t)}_{i,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
\end{remark}

@@

\subsection{Linear-Combination Aggregator Oblivious Encryption} \label{subsec:lcao}
We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$. These are used by a trusted third party, an aggregator and value producing users $i,\,1\leq i \leq n$. They are defined as follows

\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the number of weights $m$, the aggregator's public and private keys $pk_0$ and $sk_0$, and the user private keys $sk_i,\,1\leq i \leq n$.
    \item[$\mathsf{Enc}(pk_0, x)$] The aggregator and users can encrypt any value $x$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(x)$.
    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$] At instance $t$, user $i$ computes and obtains the encrypted linear combination $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\dots,l^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
\end{LaTeXdescription}

@@

\begin{LaTeXdescription}
    \item[Setup] The challenger chooses security parameter $\kappa$, runs the $\mathsf{Setup}(\kappa)$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
    \begin{LaTeXenumerate}
        \item \textit{Encryption:} The attacker chooses a value $x$ and computes an encryption of $x$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(x)$.
        \item \textit{Weight Queries:} The attacker chooses an instance $t$ and receives the weights for that instance encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ and $(i',t',a^{\prime(t')}_{i',1},\dots,a^{\prime(t')}_{i',m})$, the following condition holds:
        \begin{equation*}
            i = i' \wedge t = t' \implies a^{(t)}_{i,j} = a^{\prime(t')}_{i',j},\,1\leq j\leq m\,.
        \end{equation*}
        The attacker is then given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{LaTeXenumerate} 
    \item[Challenge] Next, the attacker chooses an instance $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for the instance $t^*$, and no compromise queries, are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \left\langle\left(i,t^*,a^{(t^*)(0)}_{i,1},\dots,a^{(t^*)(0)}_{i,m}\right)\,\middle|\,i \in S\right\rangle
    \end{equation*}
    and
    \begin{equation*}
        \left\langle\left(i,t^*,a^{(t^*)(1)}_{i,1},\dots,a^{(t^*)(1)}_{i,m}\right)\,\middle|\, i \in S\right\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.} the aggregator is compromised) and $S = U$, it is additionally required that
    \begin{equation*}
        \sum_{i\in S}\sum^{m}_{j=1} a^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} a^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
    \end{equation*}
    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen instance $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \left\langle\mathcal{E}_{pk_0,sk_i}\left(\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i\in S\right\rangle\,.
    \end{equation*}
    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game if and only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{LaTeXdescription}

\begin{definition}
    An encryption scheme meets LCAO security if no adversary, running in probabilistic-time with respect to security parameter $\kappa$, has more than a negligible advantage in winning the above security game. Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
\end{definition}

@@

    \For{$v \gets 1$ to $2$}
        \State Receive $\alpha_{v}^{(i)}$ from each sensor $1\leq i \leq n$
    \EndFor
